### 2023-04-18 README.qmd
Re-organise content

Raw data and analysis-ready processed data is available as an R package
at @R-qechairquality.

@@

The Quarto template for Elsevier journals was used to prepared the final
submitted PDF document.

The data underlying the tables and figures of this manuscript are
contained in:

\[TODO: Add link to data\]

>>>>

## Data

Raw data and analysis-ready processed data is available as an R package
at: https://github.com/Global-Health-Engineering/qechairquality [@R-qechairquality].

The data underlying the tables and figures of this manuscript are
contained in this repo in [data/processed-data/](https://github.com/Global-Health-Engineering/manuscript-qechairquality/tree/main/data/processed-data).

## Figures

## Software

@@

The [Quarto template for Elsevier journals](https://github.com/quarto-journals/elsevier) was used to prepared the final
submitted PDF document.
